---
title: "Visuals Pipeline"
author: "Laxchan Florence Angelo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pipeline

## Needed packages

```{r}
library(tidyverse)
library(gridExtra)
library(here)
library(gtsummary)
```

## Build realtive Path to the .csv files

### Global Paths
```{r}
here() # shows the path we are at currently
data_from <- here("my_work", "dnns", "Auswertung") #Build path to the data you want to plot
```

### Diverse file extraction for flat plots across models

```{r}
diverse <-  dir(path = data_from,
                  pattern="*diverse.csv$") #double backslash to make dot match literal dot (default dot= any), $ matches end 
diverse_csv <- paste0(data_from, "/", diverse) # build paths to each file 
diverse_files <- map(diverse_csv, \(x) read_csv(x)) # Map every csv data to a list
names(diverse_files) <- gsub("\\_diverse.csv$", "", diverse) # Name list of data according 
diverse_files
```

### Prototype file extraction for flat plots across models

```{r}
prototype <-  dir(path = data_from,
                  pattern="*prototype.csv$") #double backslash to make dot match literal dot (default dot= any), $ matches end
prototype_csv <- paste0(data_from, "/", prototype) # build paths to each file 
prototype_files <- map(prototype_csv, \(x) read_csv(x)) # Map every csv data to a list
names(prototype_files) <- gsub("\\_prototype.csv$", "", prototype) # Name list of data according
```

# Data preparation

## Diverse

```{r}
diverse_training <- map(diverse_files, \(x) filter(x, phase=="train") %>% #Extract training Data
               group_by(run, epoch) %>% #Group dataset into 20 runs and in every run make groups of 6 because of epochs
               mutate(hit = if_else(ground_truth == prediction, 1, 0), # 1 if Predictions is equal to ground truth, else 0
           nr_of_hits_in_this_epoch= cumsum(hit == 1), # Count right predicions on the go 
           trials= seq_along(along.with = epoch), # Count number of pictures shown to architecture in respective epoch
           running_percentage = nr_of_hits_in_this_epoch/trials, # Calculate acuracy after each picture
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials))) # Calculate avg accuracy in each epoch 

diverse_training_sliced <- map(diverse_training, \(x) slice(x, max(trials))) #slicing last computed accuracy per epoch 


diverse_train_epoch_avg <- map(diverse_training_sliced, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())


diverse_testing <- map(diverse_files, \(x) filter(x, phase=="test") %>%
               group_by(run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials))) 


diverse_testing_sliced <- map(diverse_testing, \(x) slice(x, max(trials)))

diverse_test_epoch_avg <- map(diverse_testing_sliced, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

```

## Prototype

```{r}
prototype_training <- map(prototype_files, \(x) filter(x, phase=="train") %>% #Extract training Data
               group_by(run, epoch) %>% #Group dataset into 20 runs and in every run make groups of 6 because of epochs
               mutate(hit = if_else(ground_truth == prediction, 1, 0), # 1 if Predictions is equal to ground truth, else 0
           nr_of_hits_in_this_epoch= cumsum(hit == 1), # Count right predicions on the go 
           trials= seq_along(along.with = epoch), # Count number of pictures shown to architecture in respective epoch
           running_percentage = nr_of_hits_in_this_epoch/trials, # Calculate acuracy after each picture
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials))) # Calculate avg accuracy in each epoch 

prototype_training_sliced <- map(prototype_training, \(x) slice(x, max(trials))) #slicing last computed accuracy per epoch 


prototype_train_epoch_avg <- map(prototype_training_sliced, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())


prototype_testing <- map(prototype_files, \(x) filter(x, phase=="test") %>%
               group_by(run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials))) 


prototype_testing_sliced <- map(prototype_testing, \(x) slice(x, max(trials)))

prototype_test_epoch_avg <- map(prototype_testing_sliced, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

```

# Make plots with accuracy across models.

## Diverse accuracy

```{r}
diverse_flat_train_epoch_avg <- diverse_train_epoch_avg %>%
  imap_dfr(~ tibble(
    model = .y,
    epoch = .x$epoch,
    accuracy = .x$avg
  ))

diverse_across_training <- ggplot(diverse_flat_train_epoch_avg, aes(x= as.factor(epoch), y = accuracy, colour = as.factor(model), group = model)) +
    geom_point(size = 3)+
         geom_line()+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("DNN Training: Diverse"))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))

diverse_flat_test_epoch_avg <- diverse_test_epoch_avg %>%
  imap_dfr(~ tibble(
    model = .y,
    epoch = .x$epoch,
    accuracy = .x$avg
  ))

diverse_across_test <- ggplot(diverse_flat_test_epoch_avg, aes(x= as.factor(epoch), y = accuracy, colour = as.factor(model), group = model)) +
    geom_point(size = 3)+
         geom_line()+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("DNN Testing: Diverse"))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))
```

## Prototype

```{r}
prototype_flat_train_epoch_avg <- prototype_train_epoch_avg %>%
  imap_dfr(~ tibble(
    model = .y,
    epoch = .x$epoch,
    accuracy = .x$avg
  ))

prototype_across_training <- ggplot(prototype_flat_train_epoch_avg, aes(x= as.factor(epoch), y = accuracy, colour = as.factor(model), group = model)) +
    geom_point(size = 3)+
         geom_line()+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("DNN Training: Prototype"))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))

prototype_flat_test_epoch_avg <- prototype_test_epoch_avg %>%
  imap_dfr(~ tibble(
    model = .y,
    epoch = .x$epoch,
    accuracy = .x$avg
  ))

prototype_across_test <- ggplot(prototype_flat_test_epoch_avg, aes(x= as.factor(epoch), y = accuracy, colour = as.factor(model), group = model)) +
    geom_point(size = 3)+
         geom_line()+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("DNN Testing: Prototype"))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))
```

# Final products

## Training

### Diverse:
```{r}
diverse_across_training
```

### Prototype:
```{r}
prototype_across_training
```

## Testing

### Diverse:
```{r}
diverse_across_test
```

### Prototpe:
```{r}
prototype_across_test
```
# Save as .png

```{r}

library(patchwork)
wrap_plots(Training_accuracy_plots) %>% 
   ggsave(filename="Training_accuracy_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

wrap_plots(Testing_accuracy_plots) %>% 
   ggsave(filename="Testing_accuracy_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

wrap_plots(ood1_plots) %>% 
   ggsave(filename="ood1_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(ood2_plots) %>% 
   ggsave(filename="ood2_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(ood3_plots) %>% 
   ggsave(filename="ood3_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(iid_plots) %>% 
   ggsave(filename="iid_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

```
