---
title: "Visuals Pipeline"
author: "Laxchan Florence Angelo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pipeline

## Needed packages
```{r}
library(tidyverse)
library(gridExtra)
library(here)
library(gtsummary)
library(patchwork)
library(cowplot)
library(dplyr)
library(boot)
library(purrr)
library(stringr)
library(tidyr)
library(gt)
library(viridis)
```


#Relative Pfad zu CSV bauen in Daten_von
```{r}

here() # shows the path we are at currently

data_from <- here("my_work", "dnns", "Auswertung") #Build path to the data you want to plot

temporary <-  dir(path = data_from,
                  pattern="\\.csv$") #double backslash to make dot match literal dot (default dot= any), $ matches end of string

Paths_csv <- paste0(data_from, "/", temporary) # build paths to each file 

myfiles <- map(Paths_csv, \(x) read_csv(x)) # Map every csv data to a list

names(myfiles) <- gsub("\\.csv$", "", temporary) # Name list of data according 

myfiles

```


### Data preparation
```{r}
training <- map(myfiles, \(x) filter(x, phase=="train") %>% #Extract training Data
               group_by(run, epoch) %>% #Group dataset into 20 runs and in every run make groups of 6 because of epochs
               mutate(hit = if_else(ground_truth == prediction, 1, 0), # 1 if Predictions is equal to ground truth, else 0
                      trials = seq_along(epoch),
           percentage_epochs = mean(hit))) # Calculate avg accuracy in each epoch 

train_epoch_avg <- map(training, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

training_sliced <- map(training, \(x) slice(x, max(trials)))

testing <- map(myfiles, \(x) filter(x, phase=="test") %>%
               group_by(run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
                      trials = seq_along(epoch),
              percentage_epochs = mean(hit))) 


testing_sliced <- map(testing, \(x) slice(x, max(trials)))

test_epoch_avg <- map(testing_sliced, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

```


## List of Plots
### Accuracy Training Plots
```{r eval=FALSE, include=FALSE}
name_training <- names(training) %>% 
  str_replace(pattern = "_", replacement = " \nTrainingsphase: ")

#Pretty machen
Training_accuracy_plots <- pmap(list(training_sliced, name_training, train_epoch_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1,
                                                                                                              seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
        theme(legend.position="none")
      )
```

### Accuracy Testing Plots
```{r eval=FALSE, include=FALSE}
name_testing <- names(testing) %>% 
  str_replace(pattern = "_", replacement = " \nTestphase: ")

Testing_accuracy_plots <- pmap(list(testing_sliced, name_testing, test_epoch_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1, seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
       theme(legend.position="none")
     )
```

#testing analyze
```{r eval=FALSE, include=FALSE}
ood1 <- ".ood1" 
ood1bool <- map(myfiles, \(x) pull(x, image_name) %>%  str_detect(ood1))
ood1_raw <- map2(myfiles, ood1bool, \(x,y) ungroup(x) %>% filter(y))


ood2 <- ".ood2" 
ood2bool <- map(myfiles, \(x) pull(x, image_name) %>%  str_detect(ood2))
ood2_raw <- map2(myfiles, ood2bool, \(x,y) ungroup(x) %>% filter(y))


ood3 <- ".ood3" 
ood3bool <- map(myfiles, \(x) pull(x, image_name) %>%  str_detect(ood3))
ood3_raw <- map2(myfiles, ood3bool, \(x,y) ungroup(x) %>% filter(y))


iid <- ".iid" 
iidbool <- map(myfiles, \(x) pull(x, image_name) %>%  str_detect(iid))
iid_raw <- map2(myfiles, iidbool, \(x,y) ungroup(x) %>% filter(y))


ood1_data <- map(ood1_raw, \(x) group_by(x, run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials)))

ood2_data <- map(ood2_raw, \(x) group_by(x, run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials)))

ood3_data <- map(ood3_raw, \(x) group_by(x, run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials)))

iid_data <- map(iid_raw, \(x) group_by(x, run, epoch) %>%
               mutate(hit = if_else(ground_truth == prediction, 1, 0),
           nr_of_hits_in_this_epoch= cumsum(hit == 1), 
           trials= seq_along(along.with = epoch), 
           running_percentage = nr_of_hits_in_this_epoch/trials, 
           percentage_epochs = max(nr_of_hits_in_this_epoch) / max(trials)))



ood1_slice <- map(ood1_data, \(x) slice(x, max(trials)))

ood2_slice <- map(ood2_data, \(x) slice(x, max(trials)))

ood3_slice <- map(ood3_data, \(x) slice(x, max(trials)))

iid_slice <- map(iid_data, \(x) slice(x, max(trials)))


ood1_avg <- map(ood1_slice, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

ood2_avg <- map(ood2_slice, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

ood3_avg <- map(ood3_slice, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())

iid_avg <- map(iid_slice, \(x) select(x, run, epoch, percentage_epochs) %>% 
      group_by(epoch) %>% 
      mutate(avg = mean(percentage_epochs)) %>% select(epoch, avg) %>% 
    unique())
```

```{r eval=FALSE, include=FALSE}

name_ood1 <- names(testing) %>% 
  str_replace(pattern = "_", replacement = " \nCategory: OOD1 \nTestphase: ")

ood1_plots <-  pmap(list(ood1_slice, name_ood1, ood1_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1, seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
        theme(legend.position="none")
      )
 
 name_ood2 <- names(testing) %>% 
  str_replace(pattern = "_", replacement = " \nCategory: OOD2 \nTestphase: ")

ood2_plots <-  pmap(list(ood2_slice, name_ood2, ood2_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1, seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
        theme(legend.position="none")
      )
 
 name_ood3 <- names(testing) %>% 
  str_replace(pattern = "_", replacement = " \nCategory: OOD3 \nTestphase: ")

ood3_plots <-  pmap(list(ood3_slice, name_ood3, ood3_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1, seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
        theme(legend.position="none")
      )
 
 name_iid <- names(testing) %>% 
  str_replace(pattern = "_", replacement = " \nCategory: IID \nTestphase: ")

iid_plots <-  pmap(list(iid_slice, name_iid, iid_avg), \(x, y, z) ggplot(x, aes(x=as.factor(epoch)))+
         geom_point(data = x, aes(y= percentage_epochs, colour= as.factor(epoch)), position = position_jitter(width = 0.1, seed = 42))+
       geom_point(data = z, aes(y= avg, x=as.factor(epoch)), shape=6)+
         geom_line(data = z, aes(x=epoch, y= avg, colour= "red"))+
        geom_hline(yintercept = 1/3, colour = "black", size = 1)+
       theme_bw()+
      labs(title = paste0("Architecture: ", y))+
        xlab(label = "Epoch")+
        ylab(label = "Accuracy")+
        scale_y_continuous(expand = c(0, 0), limits = c(0,1.1))+
        theme(legend.position="none")
      )
```

# Saving Plots as png

```{r eval=FALSE, include=FALSE}

library(patchwork)
wrap_plots(Training_accuracy_plots) %>% 
   ggsave(filename="Training_accuracy_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

wrap_plots(Testing_accuracy_plots) %>% 
   ggsave(filename="Testing_accuracy_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

wrap_plots(ood1_plots) %>% 
   ggsave(filename="ood1_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(ood2_plots) %>% 
   ggsave(filename="ood2_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(ood3_plots) %>% 
   ggsave(filename="ood3_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern


wrap_plots(iid_plots) %>% 
   ggsave(filename="iid_plots.png", 
        height = 40,
        width = 40,
        units = "cm") #hier Name ändern

```

##Show all results in one Plot
## Bootstrap confidence intervalls
```{r}
library(dplyr)
library(purrr)
library(tibble)
library(boot)
library(ggplot2)

# ----------------------------------------
# Define bootstrap function (per group)
boot_accuracy <- function(data, indices) {
  sampled_data <- data[indices, ]
  mean(sampled_data$hit)
}


bootstrap_group <- function(df_group, R = 1000) {
  boot_res <- boot(df_group, boot_accuracy, R = R)
  ci <- boot.ci(boot_res, type = "perc")
  tibble(
    epoch = unique(df_group$epoch),
    acc = mean(df_group$hit),
    ci_lower = ci$percent[4],
    ci_upper = ci$percent[5]
  )
}

# ----------------------------------------
# Function to process each architecture dataframe
set.seed(42)

bootstrap_architecture <- function(df_arch, arch_name, R = 1000) {
  df_arch %>%
    group_by(epoch) %>%
    group_split() %>%
    map_dfr(~bootstrap_group(.x, R = R)) %>%
    mutate(architecture = arch_name)
}

# ----------------------------------------
# General function to process full list
process_list <- function(data_list, R = 1000) {
  # Extract architecture names from list names
  arch_names <- names(data_list)
  
  # Apply bootstrap function across list
  map2_dfr(data_list, arch_names, ~bootstrap_architecture(.x, .y, R = R))
}

# ----------------------------------------
# Now apply to your two lists:

# Example:
# train_list <- list(alexnet_diverse = ..., resnet_prototype = ..., etc.)
# test_list <- list(...)

# Compute results for train and test
train_results <- process_list(training, R = 1000) %>%
  mutate(phase = "train") %>% group_by(architecture) %>% nest()

test_results <- process_list(testing, R = 1000) %>%
  mutate(phase = "test") %>% group_by(architecture) %>% nest()

# Combine both into one dataframe
full_results <- bind_rows(train_results, test_results)

```



# ```{r}
# ggplot(full_results, aes(x = epoch, y = acc, color = phase)) +
#   geom_line() +
#   geom_point() +
#   geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper, fill = phase), alpha = 0.2) +
#   geom_hline(yintercept = 1/3, linetype = "dashed", color = "black") +
#   facet_wrap(~architecture, scales = "free_y") +
#   theme_minimal(base_size = 16)
# 
# ```

```{r}
set.seed(42)

##in work
name_training <- names(training) %>% 
  str_replace(pattern = "_", replacement = " \nTraining data: ")


name_training[3] <- "default alexnet \nTraining data: prototype"
name_training[6] <- "default convnext \nTraining data: prototype"
name_training[9] <- "default efficientnet \nTraining data: prototype"
name_training[12] <- "default resnet \nTraining data: prototype" 
name_training[15] <- "default vgg16 \nTraining data: prototype"  

final_plots <- pmap(
  list(name_training, training_sliced, testing_sliced, train_results$data, test_results$data, train_epoch_avg, test_epoch_avg),
  \(x, y, z, a, b, c, d){
    ggplot() +
      # Jittered points for training
      geom_jitter(data = y, 
                  aes(x = as.factor(epoch), y = percentage_epochs, color = "Train"), 
                  width = 0.1, alpha = 0.5, size = 1.5) +
      # Jittered points for Test
      geom_jitter(data = z, 
                  aes(x = as.factor(epoch), y = percentage_epochs, color = "Test"), 
                  width = 0.1, alpha = 0.5, size = 1.5) +
      
      # Training average points
      geom_point(data = c,
                 aes(x = as.factor(epoch), y = avg, shape = "Train"),
                 color = "#0072B2", size = 3) +
      
      # Test average points
      geom_point(data = d,
                 aes(x = as.factor(epoch), y = avg, shape = "Test"),
                 color = "#D55E00", size = 3) +
      # Training value label at epoch 6
geom_text(data = filter(c, epoch == 6),
          aes(x = as.factor(epoch), y = avg, label = sprintf("%.2f", avg)),
          vjust = 2, hjust=1, color = "#0072B2", fontface = "bold", size = 5) +

# Test value label at epoch 6
geom_text(data = filter(d, epoch == 6),
          aes(x = as.factor(epoch), y = avg, label = sprintf("%.2f", avg)),
          vjust = 2, hjust=1,  color = "#D55E00", fontface = "bold", size = 5) +


      # Confidence intervals (ribbons)
      geom_ribbon(data = a, aes(x = epoch, y = acc, ymin = ci_lower, ymax = ci_upper, fill = "Train"), alpha = 0.3) +
      geom_ribbon(data = b, aes(x = epoch, y = acc, ymin = ci_lower, ymax = ci_upper, fill = "Test"), alpha = 0.3) +

      # Horizontal benchmark line
      geom_hline(yintercept = 1/3, colour = "red", size = 1, linetype = "dashed") +
      
      # Color legend for jittered points
      scale_color_manual(
        values = c(
          "Train" = "#56B4E9",  # lighter blue for jitter
          "Test"  = "#E69F00"   # lighter orange for jitter
        ),
        name = "Empirical Data (20 runs):"
      ) +

      # Shape legend for averages
      scale_shape_manual(
        values = c("Train" = 17, "Test" = 15),
        name = "Averages per Epoch:"
      ) +

      # Fill legend for confidence intervals
      scale_fill_manual(
        values = c(
          "Train" = scales::alpha("#0072B2", 0.3),
          "Test"  = scales::alpha("#D55E00", 0.3)
        ),
        name = "95% CI (bootstrap, n=1000):"
      ) +

      theme_gray(base_size = 14) +
      labs(
        title = paste0("Architecture: ", x),
        x = "Epoch",
        y = "Accuracy"
      ) +
      scale_y_continuous(expand = c(0, 0), limits = c(0, 1.1)) +
      theme(
        legend.title = element_text(size=14, face = "bold"),
        legend.text = element_text(size=14, face = "bold"),
        legend.position = "top",
        legend.box = "horizontal",
        panel.grid.minor = element_blank(),
        axis.text = element_text(face="bold"),
        axis.text.x = element_text(face="bold", size=12),
        axis.text.y = element_text(face="bold", size=12),
        axis.title = element_text(size=12, face="bold"),
        plot.title = element_text(size=12, face="bold")
      )
  }
)

final_plots[1]
```

## Save oben
```{r}
p <- wrap_plots(final_plots)+plot_layout(guides='collect', ncol = 3) & theme(legend.box.background = element_rect(),
        legend.box.margin = margin(6, 6, 6, 6),
         legend.position = "bottom")

 
p %>% 
ggsave(dpi = 300,
       filename="final_default_trend_proto_plots.png", 
        height = 40,
        width = 38,
        units = "cm") #hier Name ändern
```

## table
```{r}
# Initialisieren
i = 1
name_vector = c()
training_accuracy = c()

for(x in train_epoch_avg){
  name_vector[i] <- names(train_epoch_avg)[i]
  temp <- x %>% ungroup() %>% select(avg) %>% slice(6) %>% as.double()
  training_accuracy[i] <- temp
  i <- i + 1
}

i = 1
testing_accuracy = c()

for(x in test_epoch_avg){
  name_vector[i] <- names(test_epoch_avg)[i]
  temp <- x %>% ungroup() %>% select(avg) %>% slice(6) %>% as.double()
  testing_accuracy[i] <- temp
  i <- i + 1
}

# Zusammenführen
df <- data.frame(name_vector, training_accuracy, testing_accuracy)

# Architektur extrahieren
df <- df %>%
  mutate(architecture = str_extract(name_vector, "^[^_]+"))

# Zusammenfassung berechnen
df_summary <- df %>%
  group_by(architecture) %>%
  summarise(mean_training = mean(training_accuracy, na.rm = TRUE),
            mean_testing = mean(testing_accuracy, na.rm = TRUE)) %>%
  ungroup()

# Tabelle in gewünschtes Format bringen
df_long <- df_summary %>%
  pivot_longer(cols = c(mean_training, mean_testing),
               names_to = "metric",
               values_to = "mean_accuracy") %>%
  mutate(metric = recode(metric,
                         "mean_training" = "Training phase",
                         "mean_testing" = "Testing phase")) %>%
  pivot_wider(names_from = architecture, values_from = mean_accuracy) %>%
  rename(`Mean Accuracy` = metric)

df_long <- add_row(df_long,
                   `Mean Accuracy` = "Model weights",
                   alexnet = 57016131,
                   convnext = 87569539,
                   efficientnet =52862199,
                   resnet = 23514179,
                   vgg16 = 134272835)
```


```{r}
# Tabelle mit gt darstellen
my_table <- df_long %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric),
    decimals = 4
  ) %>%
  fmt_number(
    columns = where(is.numeric),
    rows = nrow(df_long),  # last row by row index
    decimals = 0,
    use_seps = TRUE
  ) %>%
  cols_align(
    align = "left",
    columns = where(is.numeric)
  ) %>%
  tab_header(
    title = "Mean accuracy and architecture size"
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    heading.title.font.size = 12,
    heading.subtitle.font.size = 10,
    table.font.size = 11,
    column_labels.font.weight = "bold",
    data_row.padding = px(4)
  )


gtsave(my_table, "model_performance.png")
```

```{r}
# Extract parameters row
param_row <- df_long %>%
  filter(`Mean Accuracy` == "Model weights") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

# Extract training and testing rows
train_row <- df_long %>%
  filter(`Mean Accuracy` == "Training phase") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

test_row <- df_long %>%
  filter(`Mean Accuracy` == "Testing phase") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

# Calculate Pearson correlations
cor_train <- cor(param_row, train_row, use = "complete.obs", method = "pearson")
cor_test <- cor(param_row, test_row, use = "complete.obs", method = "pearson")

```
# Training D/P individuell
```{r}
# loop d/p je CNN zusm zu nehmen
lop <- c(1,3,5,7,9)
for (x in lop) {
  x+1
  result <- bind_rows(train_epoch_avg[[x]], train_epoch_avg[[x + 1]]) %>% 
    group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg)
  
  # Assign result to architecture_1, architecture_2, etc.
  assign(paste0("architecture_", x), result)
}
architecture_9
# berechne abs differenz
for (x in lop) {
  var_name <- paste0("architecture_", x)
  
  # Get the actual data frame by name using get()
  df <- get(var_name)
  
  # Modify it
  df <- df %>% mutate(difference = abs(condition1 - condition2))
  
    # Rename the columns
  colnames(df) <- c("Epoch", "Diverse", "Prototype", "Absolute difference")
  
  # Assign it back to the original variable name
  assign(var_name, df)
}

# Loop um einzelne Tbl zu speichern
for (i in lop) {
  var_name <- paste0("architecture_", i)
  df <- get(var_name)
  
  # Create gt table
  gt_table <- df %>%
  pivot_longer(
    cols = -Epoch,
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  pivot_wider(names_prefix = "Epoch ",
    names_from = Epoch,
    values_from = Value) %>% 
    gt() %>%
    fmt_number(decimals = 3)  %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) %>%
    opt_table_outline() %>%
    opt_row_striping()

    # Save gt table as PNG
  gtsave(gt_table, filename = paste0("architecture_training_", i, ".png"))
}
```
# Training D/P avg
```{r}
# full join alle diversen und berechne avg
  diverse_set <- full_join(train_epoch_avg[[1]], train_epoch_avg[[3]]) %>% 
  full_join(train_epoch_avg[[5]]) %>% 
  full_join(train_epoch_avg[[7]]) %>% 
  full_join(train_epoch_avg[[9]]) %>% 
   group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg) %>%         mutate(diverse = rowMeans(cbind(condition1, condition2, condition3, condition4, condition5))) %>% 
  select(epoch, diverse)

# full join alle proto und berechne avg
  prototype_set<- full_join(train_epoch_avg[[2]], train_epoch_avg[[4]]) %>% 
  full_join(train_epoch_avg[[6]]) %>% 
  full_join(train_epoch_avg[[8]]) %>% 
  full_join(train_epoch_avg[[10]]) %>% 
   group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg) %>% 
    mutate(prototype = rowMeans(cbind(condition1, condition2, condition3, condition4, condition5))) %>% 
    select(epoch, prototype)

  # abs differenz zwischen avg berechnen
  comparison <- 
  full_join(diverse_set, prototype_set) %>% 
    mutate("Absolute difference" = abs(diverse - prototype))

  # umbenennen so dass wie indi passt
    colnames(comparison) <- c("Epoch", "Diverse", "Prototype", "Absolute difference")
    
    # speicchere plots 
    comparison %>%   pivot_longer(
    cols = -Epoch,
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  pivot_wider(names_prefix = "Epoch ",
    names_from = Epoch,
    values_from = Value) %>% 
    gt() %>%
    fmt_number(decimals = 3)%>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) %>%
    opt_table_outline() %>%
    opt_row_striping() %>% 
  # Save gt table as PNG
  gtsave(filename = "d_p_training_comparison.png")


  
```

```{r}
# Tabelle mit gt darstellen
my_table <- df_long %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric),
    decimals = 4
  ) %>%
  fmt_number(
    columns = where(is.numeric),
    rows = nrow(df_long),  # last row by row index
    decimals = 0,
    use_seps = TRUE
  ) %>%
  cols_align(
    align = "left",
    columns = where(is.numeric)
  ) %>%
  tab_header(
    title = "Mean accuracy and architecture size"
  ) %>%
  tab_options(
    table.font.names = "Times New Roman",
    heading.title.font.size = 12,
    heading.subtitle.font.size = 10,
    table.font.size = 11,
    column_labels.font.weight = "bold",
    data_row.padding = px(4)
  )


gtsave(my_table, "model_performance.png")
```

```{r}
# Extract parameters row
param_row <- df_long %>%
  filter(`Mean Accuracy` == "Model weights") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

# Extract training and testing rows
train_row <- df_long %>%
  filter(`Mean Accuracy` == "Training phase") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

test_row <- df_long %>%
  filter(`Mean Accuracy` == "Testing phase") %>%
  select(-`Mean Accuracy`) %>%
  unlist() %>%
  as.numeric()

# Calculate Pearson correlations
cor_train <- cor(param_row, train_row, use = "complete.obs", method = "pearson")
cor_test <- cor(param_row, test_row, use = "complete.obs", method = "pearson")

```
# Testing D/P individuell
```{r}
# loop d/p je CNN zusm zu nehmen
lop <- c(1,3,5,7,9)
for (x in lop) {
  result <- bind_rows(test_epoch_avg[[x]], test_epoch_avg[[x + 1]]) %>% 
    group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg)
  
  # Assign result to architecture_1, architecture_2, etc.
  assign(paste0("architecture_", x), result)
}

# berechne abs differenz
for (x in lop) {
  var_name <- paste0("architecture_", x)
  
  # Get the actual data frame by name using get()
  df <- get(var_name)
  
  # Modify it
  df <- df %>% mutate(difference = abs(condition1 - condition2))
  
    # Rename the columns
  colnames(df) <- c("Epoch", "Diverse", "Prototype", "Absolute difference")
  
  # Assign it back to the original variable name
  assign(var_name, df)
}

# Loop um einzelne Tbl zu speichern
for (i in lop) {
  var_name <- paste0("architecture_", i)
  df <- get(var_name)
  
  # Create gt table
  gt_table <- df %>%
  pivot_longer(
    cols = -Epoch,
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  pivot_wider(names_prefix = "Epoch ",
    names_from = Epoch,
    values_from = Value) %>% 
    gt() %>%
    fmt_number(decimals = 3)  %>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) %>%
    opt_table_outline() %>%
    opt_row_striping()

    # Save gt table as PNG
  gtsave(gt_table, filename = paste0("architecture_testing_", i, ".png"))
}
```
# Training D/P avg
```{r}
# full join alle diversen und berechne avg
  diverse_set <- full_join(test_epoch_avg[[1]], test_epoch_avg[[3]]) %>% 
  full_join(test_epoch_avg[[5]]) %>% 
  full_join(test_epoch_avg[[7]]) %>% 
  full_join(test_epoch_avg[[9]]) %>% 
   group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg) %>%         mutate(diverse = rowMeans(cbind(condition1, condition2, condition3, condition4, condition5))) %>% 
  select(epoch, diverse)

# full join alle proto und berechne avg
  prototype_set<- full_join(test_epoch_avg[[2]], test_epoch_avg[[4]]) %>% 
  full_join(test_epoch_avg[[6]]) %>% 
  full_join(test_epoch_avg[[8]]) %>% 
  full_join(test_epoch_avg[[10]]) %>% 
   group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg) %>% 
    mutate(prototype = rowMeans(cbind(condition1, condition2, condition3, condition4, condition5))) %>% 
    select(epoch, prototype)

  # abs differenz zwischen avg berechnen
  comparison <- 
  full_join(diverse_set, prototype_set) %>% 
    mutate("Absolute difference" = abs(diverse - prototype))

  # umbenennen so dass wie indi passt
    colnames(comparison) <- c("Epoch", "Diverse", "Prototype", "Absolute difference")
    
    # speicchere plots 
    comparison %>%   pivot_longer(
    cols = -Epoch,
    names_to = "Metric",
    values_to = "Value"
  ) %>%
  pivot_wider(names_prefix = "Epoch ",
    names_from = Epoch,
    values_from = Value) %>% 
    gt() %>%
    fmt_number(decimals = 3)%>%
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_column_labels(everything())
    ) %>%
    opt_table_outline() %>%
    opt_row_striping() %>% 
  # Save gt table as PNG
  gtsave(filename = "d_p_testing_comparison.png")


  
```
#trouble shooting
```{r}
  full_join(test_epoch_avg[[9]], test_epoch_avg[[10]]) %>% 
    group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg)


bind_rows(
  test_epoch_avg[[9]],
  test_epoch_avg[[10]])%>% 
      group_by(grp = cumsum(epoch == 1)) %>%
    mutate(row = row_number()) %>%
    ungroup() %>%
    select(-row) %>%
    mutate(run = paste0("condition", grp)) %>%
    select(-grp) %>%
    pivot_wider(names_from = run, values_from = avg)

```
## hp optim loading
```{r}
# step back in parent dir für file
setwd("..")
neuer_root <- getwd()
temp <- dir(pattern="\\.csv$")

Paths_to_csv <- paste0(neuer_root, "/", temp) # build paths to each file 

all_optuna_files <- map(Paths_to_csv, \(x) read_csv(x)) # Map every csv data to a list

names(all_optuna_files) <- gsub("\\.csv$", "", temp) # Name list of data according 

all_optuna_files
```
##hp optim prepare
```{r}
optuna_files <- all_optuna_files[1:3]

prototype_index <- c(2,4,6,8,10)
diverse_index <- c(1,3,5,7,9)


optuna_files <- all_optuna_files[prototype_index]

optuna_labeled <- map2(optuna_files, names(optuna_files), \(x, y) mutate(x, algorithm = as.factor(params_algorithm)) %>%
    select(value, algorithm, params_dropout_rate) %>%
    mutate(dataset = y))

# Combine into one tibble
optuna_combined <- bind_rows(optuna_labeled)

optuna_combined$dataset <- sub("_.*", "", optuna_combined$dataset)


hp_combined <- optuna_combined %>%
  group_by(dataset) %>%
  slice_max(order_by = value, n = 1, with_ties = FALSE) %>%
  ungroup()

optuna_combined

optuna_combined <- optuna_combined %>%
  anti_join(hp_combined, by = colnames(optuna_combined)) %>% 
  filter(!is.na(algorithm))


```

## hp plotting
```{r}
boxplots <- ggplot() +
  # Boxplots
  geom_boxplot(data = optuna_combined, aes(x = dataset, y = value), outlier.shape = NA, fill = "gray90") +
  
    # Highlight best trials
  geom_point(
    data = hp_combined,
    aes(x = dataset, y = value, shape = algorithm),
    color = "red",
    size = 3,
    show.legend = FALSE# a distinct shape like star or diamond
  ) +
  
  # Jittered scatter points
  geom_point(
    data = optuna_combined,
    aes(x = dataset, y = value, shape = algorithm, colour = params_dropout_rate),
    position = position_jitter(width = 0.10),
    alpha = 0.6,
    size = 2
  ) +

  

  
  
  # Optional: Scales for color/shape
  scale_color_viridis_c(option = "D") +
  scale_shape_manual(values = c(16, 17, 18, 15)) +  # customize per your algorithms
  
  # Themes and labels
  theme_minimal(base_size = 14) +
  labs(
    x = "Prototype",
    y = "Accuracy (%)",
    colour = "Dropout Rate",
    shape = "Algorithm",
  ) +
  theme(
    legend.position = "right")+
  scale_y_continuous(limits = c(20,90) )


boxplots
```
## save box
```{r}

ggsave(
  filename = "diverse_boxplots.png", 
  plot = boxplots,
  dpi = 300,
  height = 15,
  width = 15,
  units = "cm",
  bg="white"
)
```
## get mid 
```{r}
d <- all_optuna_files

median_list <- map(d, \(x) median(x$value, na.rm = TRUE))

map2(d, median_list, \(x,y) filter(x, value == y) %>% slice(1))

```

